Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-12-01 workflow/workflow.Rmd
update with new version and plotFeatureBoxplot

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
if(packageVersion("zinbwave")<"0.99.6") stop("must have current devel version to avoid bugs")
if(packageVersion("clusterExperiment")<"1.5.0-9006") stop("must have current devel version to avoid bugs")
if(packageVersion("scone")<"1.1.2") stop("must have current devel version to avoid bugs")

@@

```{r boxplotReg3g, fig.width=6, fig.height=4, fig.cap="RSEC: Boxplots of the log count of gene Reg3g stratified by cluster."}
# c4 <- rep("other clusters", ncol(se))
# c4[primaryClusterNamed(dataObj) == "c4"] <- "cluster c4"
boxplot(log1p(assay(se)["Reg3g", ]) ~ primaryClusterNamed(dataObj), 
        ylab = "Reg3g log counts", cex.axis = .8, cex.lab = .8)
```

EP: not sure why needed 'c4' object. This is a useful plot and rather messy, so I might make a plotGeneBoxplot function.

>>>>

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
if(packageVersion("zinbwave")<"0.99.6") stop("must have current devel version to avoid bugs")
if(packageVersion("clusterExperiment")<"1.5.0-9007") stop("must have current devel version to avoid bugs")
if(packageVersion("scone")<"1.1.2") stop("must have current devel version to avoid bugs")

@@

```{r boxplotReg3g, fig.width=6, fig.height=4, fig.cap="RSEC: Boxplots of the log count of gene Reg3g stratified by cluster."}
# c4 <- rep("other clusters", ncol(se))
# c4[primaryClusterNamed(dataObj) == "c4"] <- "cluster c4"
# boxplot(log1p(assay(se)["Reg3g", ]) ~ primaryClusterNamed(dataObj),
#         ylab = "Reg3g log counts", cex.axis = .8, cex.lab = .8)
plotFeatureBoxplot(dataObj, whichCluster="primary", feature="Reg3g")
```

EP: not sure why needed 'c4' object. This is new function. Tell me if you run into problems.
